---
output: github_document
--- 

<!-- add all libraries before knitting -->  
  
```{r setup, include=FALSE}
library(tidyverse) 
library(here) 
library(flextable) 
library(officer)
library(patchwork)
library(deeptime)
library(divDyn)
library(brms)
library(lme4)
library(geiger)
library(infer)
library(effsize)
```

# Paleoclimate Interaction Origination

<!-- badges: start -->
[![Generic badge](https://img.shields.io/badge/Status-Published-green.svg)](https://shields.io/)
<!-- badges: end -->

This the R project to the second (potential) publication for PastKey covering paleoclimate interactions and origination probability. This repository contains all data files and code to reproduce results. All figures are made with `ggplot` and can be therefore reproduced with this repository as well. The raw fossil occurrence data set downloaded from the Paleoiology Database is unfortunately too large for this repository but is publically available on our [Figshare.com archive](https://figshare.com/articles/dataset/Raw_fossil_data/14528925).   
  
# File structure  
  
Throughout our analysis, we use the `here` package to structure our data files, which is based on the root directory of the *Rproj* file. We recommend to either download the entire project or to fork the repository to keep the directories tidy. If done so, it is not needed to set working directories manually. All files will work correctly without changing anything in the code. Every folder contains a README with further instructions and explanations on individual files.    
  
## R  
  
This folder contains all R code as scripts.  
  
## data  
  
This folder contains both raw and processed files, as well as results saved as *RData* or *csv* files. 
  
## figures  
  
This folder contains all figures from the main text and the supplementary information file, as well as supplementary tables.  

  
  
# Version info  
  
Information about the operating system used to run the analysis and all R packages including their dependencies and version info used throughout the R-scripts:  
  
```{r}
sessionInfo()
```

